Quality Definitions of Qualities

### 2019-12-04 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated consistency

\wss{The definition from \citet{IEEE1998} might again be useful.  We could also
  look for definitions outside of software development.  Even a dictionary
  definition could be helpful.}

>>>>

\begin{defn}
Consistency refers to internal consistency. If an SRS does not agree with some
higher-level document, such as a system requirements specification, then it is
not correct \citep{IEEE1998}.
\end{defn}
\begin{defn}
An SRS is internally consistent if, and only if, no subset of individual
requirements described in it conflict. The three types of likely conflicts in an
SRS are as follows \citep{IEEE1998}:
	\begin{enumerate}[a)]
\item The specified characteristics of real-world objects may conflict. For
example,
	\begin{enumerate}[1)]
\item The format of an output report may be described in one requirement as
tabular but in another as textual.
\item One requirement may state that all lights shall be green while another may
state that all lights shall be blue.
	\end{enumerate}
\item There may be logical or temporal conflict between two specified actions.
For example,
	\begin{enumerate}[1)]
\item One requirement may specify that the program will add two inputs and
another may specify that the program will multiply them.
\item One requirement may state that “A” must always follow “B,” while another
may require that “A and B” occur simultaneously.
	\end{enumerate}
\item Two or more requirements may describe the same real-world object but use
different terms for that object. For example, a program’s request for a user
input may be called a “prompt” in one requirement and a “cue” in another. The
use of standard terminology and definitions promotes consistency.
	\end{enumerate}
\end{defn}
\begin{defn}
The state or condition of always happening or behaving in the same way
\citep{CambridgeConsistency2019}.
\end{defn}

\wss{The definition from \citet{IEEE1998} might again be useful.  We could also
  look for definitions outside of software development.  Even a dictionary
  definition could be helpful.}
\ad{added IEEE and dictionary}
